Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-27 manuscript/manuscript.Rmd
added some discussion

>>>>

# Discussion

Fisheries are complex ecosystems, with interactions between species leading to highly non-linear dynamics.
While current models for population estimation include many important aspects of this complexity, it is still common to use simplified dynamical models in order to guide decision making.
This provides very interpretable solutions, such as constant mortality policies.
There is a drawback here, however: due to the simplicity of these dynamical models, the policies might not respond effectively in many situations---situations where the predictions of these simple models deviates considerably from reality.
Because of this, policies such as MSY have faced pushback and are believed to have contributed to the depletion of fish stocks.

We propose an alternative approach to the problem of fishery control: to use a more expressive -- albeit more complicated -- dynamical model to guide decision making.
Furthermore, rather than computing the optimal control policy for the model -- something that is impossible in practice for complex systems -- we use deep reinforcement learning to obtain a ‘‘pretty darn good’’ policy.

In this paper we have exemplified this approach by applying it to the control of a three-species fishery model.
In this example, we have shown that the DRL agent finds an approximately *bang-bang* type of solution.
While bang-bang solutions are known to be optimal for a wide variety of single-species fishery control problems [@alexandru], there is no such proof of optimality for general multi-species models.
In this sense this example is rather surprising and reassuring: while no general guarantee points at the optimality of bang-bang solutions for multi-species model, the existence of one such example provides a benchmark for the use of DRL in fishery control.

One intuition for why a constant escapement policy performs so well in such a model comes from the anticorrelation between $X$ and $Y$ noted in the results section.
We have observed in a variety of policies, both classical as well as some obtained by training DRL agents.
In all of these, the pattern has been present.
In fact, ‘‘crashes’’ in the $X$ population are almost invariably shortly preceeded by dramatic increases in $Y$.
We hypothesize that this effectively leads to a dimensionality reduction: once the value of $X$ is known, along a path traced by the control system, then $Y$ may be roughly predicted.
A similar, although weaker, anticorrelation is also observed between $X$ and $Z$.
These two informal observations point at an effective simplification of the prediction process: the values of $Y$ and $Z$ are much less impactful to policy decisions than the value of $X$ itself.
We have not yet pushed further to establish a more precise picture of this dynamical simplification.

This way, this manuscript functions as a first step in the process of incorporating DRL into fishery decision making.
Importantly, DRL is equipped with tools to deal with more complicated models which might require a more refined approach to control them.
For example *long short-term memories (LSTMs)* may be used to incorporate not only $N_t$ but also $\mathrm{d}N_t/\mathrm{d}t$ into policy decisions---while this additional degree of freedom would make analytical control theory approaches unwieldy, it may be easily and cost-effectively implemented in DRL.
Similarly, *curriculum learning* could be incorporated to deal with phenomena such as parametric noise or parametric drift [@openai].

This way, DRL provides a framework flexible enough to capture the intricate population dynamics that are relevant in fishery management.
We have shown that highly non-linear systems may give rise to simplified and good policies and that these may be found via reinforcement learning.
Moreover, the framework allows for the possibility that these simplifications do not in fact happen, and that good harvest policies are highly non-linear, multi-parameter functions.
